Adopting agile in the large: motivations, success factors and challenges

### 2014-04-23 journal/article.tex
Reasons to change: external issues

@@

Commercial competition and market situation was seen as a trigger for
transformation. Especially speed of delivery was seen as a means to respond to
the competition [P9, P38]. As Greening describes: ``The average release duration
peaked at 41 and 35 months, an alarming state that could enable competitors to
gain market share.'' [P19]. In many cases the transformation was seen as
essential for the company to remain competitive [P11, P18, P42, P49]. For
instance, British Telecom realized that ``From a strategic view, there is little
alternative than to change the old ways of working'' [P32].

@@

>>>>

\subsubsection{External issues}

@@

Commercial competition and market situation was seen as a trigger for
transformation. Especially speed of delivery was seen as a means to respond to
the competition [P9, P38]. As Greening describes: ``The average release duration
peaked at 41 and 35 months, an alarming state that could enable competitors to
gain market share.'' [P19]. In many cases the transformation was seen as
essential for the company to remain competitive [P10, P11, P18, P42, P49]. For
instance, British Telecom realized that ``From a strategic view, there is little
alternative than to change the old ways of working'' [P32].

@@

Yet another frequent external factor driving for change was the need to
accomodate change during development. Organizations saw agile as a opportunity
to improve responsiveness to change in general [P25, P26, P42].
Some organizations faced difficulties when changes to plans were needed. For
instance, the organizational struture made adapting to changes difficult [52],
and making changes created management overhead [P51]. Other organizations saw an
business advantage if priorities could be changed as required [P8, P39].
Customers and business representatives were in many cases attributed as the
sources of change requests, and the responsiveness to customer requests needed
to be improved [P18, P33, P36, P49].
